Shapes analysis for time series.

### 2024-05-22 NEURIPS24/appendix.tex
update
without societal impact
update

\section{Proofs}
\label{appendix:proofs}
Denote by $\msg(s)\triangleq \{ (t,s(t)): \eqsp t\in \msi \} $ the graph of a time series $s: \msi \to \Rset^d$ and $ \phi.\msg(s)\triangleq\{ \phi(t,s(t)): \eqsp t\in \msi\} $ the action of  $\phi\in \mcd(\Rset^{d+1}) $ on $\msg(s)$.
\begin{theorem}
    \label{theorem:representation_proof}
Let $s:  \msj \to \Rset^d  $ and $\mathbf{s}_0: \msi\to \Rset^d $ be two continuously differentiable time seriess with $\msi,\msj$ two intervals of $\Rset$.
 There exist $f\in \rmC^1(\Rset^{d+1},\Rset^d)$ and $\gamma\in  \mcd(\Rset) $ such that $\gamma(\msi)=\msj $ and $\Phi_f\in \mcd(\Rset^{d+1})$,
 \begin{equation}% TO add more detail on functionnal space
    \msg(s)= \Pi_{\gamma,f}.\msg(\mathbf{s}_0),\eqsp \Pi_{\gamma,f}=\Psi_\gamma\circ\Phi_f.
 \end{equation}
 Moreover, for any $\bar{f}\in \rmC^1(\Rset^{d+1},\Rset^d)$ and $\bar{\gamma}\in  \mcd(\Rset) $, there exists a continously differentiable time series $\bar{s}$ such that 
 $\msg(\bar{s})= \Pi_{\bar{\gamma},\bar{f}}.\msg(\mathbf{s}_0)$
\end{theorem}
%\sam{preuve todo, classement des variétés à bord, donne un homeomorphisme sur la restriction}
\begin{proof}
  Let $s:  \msj \to \Rset^d  $ and $\mathbf{s}_0: \msi\to \Rset^d $ be two continuously differentiable time seriess with $\msi=(a,b),\msj=(\alpha,\beta)$ two intervals of $\Rset$.
  By setting $\gamma: t\in \Rset \mapsto (\beta-\alpha)(t-a)/(b-a)+\alpha\in \Rset $, we have $ \gamma(\msi)=\msj$ and $\gamma \in \mcd(\Rset) $.
   By defining $f:(t,x)\in\Rset^{d+1}\mapsto x-\mathbf{s}_0(t)+s\circ \gamma(t) $, the map $\Phi_f\in \mcd(\Rset^{d+1})$,
    indeed, its inverse is $\Phi_f^{-1}:(t,x)\in\Rset^{d+1}\mapsto (t,x+\mathbf{s}_0(t)-s(t)) $ and is continuously differentiable.
     Moreover, we have $\Pi_{\gamma,f}.\msg(\mathbf{s}_0)=\{(\gamma(t),s\circ \gamma(t)):\eqsp t\in\msi \}=\msg(s) $.

>>>>

\section{Societal impact}
\label{appendix:societal_impact}
We believe that the paper has a positive societal impact for the following reasons:
\begin{itemize}
\item TS-LDDMM is an interpretable method for understanding inter-individual variability in biomedical datasets, potentially offering new insights in medicine.
\item TS-LDDMM bridges the gap between the shape analysis community and the unsupervised representation learning (URL) community, fostering potential future collaborations between these fields.
\end{itemize}
However, the computational cost of the method may raise environmental concerns similar to those associated with deep learning \cite{oh2024stable}.
 Additionally, while TS-LDDMM has promising biomedical applications, it could also be misused for creating poison.
\section{Proofs}
\label{appendix:proofs}
Denote by $\msg(s)\triangleq \{ (t,s(t)): \eqsp t\in \msi \} $ the graph of a time series $s: \msi \to \Rset^d$ and $ \phi.\msg(s)\triangleq\{ \phi(t,s(t)): \eqsp t\in \msi\} $ the action of  $\phi\in \mcd(\Rset^{d+1}) $ on $\msg(s)$.
\begin{theorem}
    \label{theorem:representation_proof}
Let $s:  \msj \to \Rset^d  $ and $\mathbf{s}_0: \msi\to \Rset^d $ be two continuously differentiable time seriess with $\msi,\msj$ two intervals of $\Rset$.
 There exist $f\in \rmC^1(\Rset^{d+1},\Rset^d)$ and $\gamma\in  \mcd(\Rset) $ such that $\gamma(\msi)=\msj $ and $\Phi_f\in \mcd(\Rset^{d+1})$,
 \begin{equation}% TO add more detail on functionnal space
    \msg(s)= \Pi_{\gamma,f}.\msg(\mathbf{s}_0),\eqsp \Pi_{\gamma,f}=\Psi_\gamma\circ\Phi_f.
 \end{equation}
 Moreover, for any $\bar{f}\in \rmC^1(\Rset^{d+1},\Rset^d)$ and $\bar{\gamma}\in  \mcd(\Rset) $, there exists a continously differentiable time series $\bar{s}$ such that 
 $\msg(\bar{s})= \Pi_{\bar{\gamma},\bar{f}}.\msg(\mathbf{s}_0)$
\end{theorem}
%\sam{preuve todo, classement des variétés à bord, donne un homeomorphisme sur la restriction}
\begin{proof}
  Let $s:  \msj \to \Rset^d  $ and $\mathbf{s}_0: \msi\to \Rset^d $ be two continuously differentiable time seriess with $\msi=(a,b),\msj=(\alpha,\beta)$ two intervals of $\Rset$.
  By setting $\gamma: t\in \Rset \mapsto (\beta-\alpha)(t-a)/(b-a)+\alpha\in \Rset $, we have $ \gamma(\msi)=\msj$ and $\gamma \in \mcd(\Rset) $.
   By defining $f:(t,x)\in\Rset^{d+1}\mapsto x-\mathbf{s}_0(t)+s\circ \gamma(t) $, the map $\Phi_f\in \mcd(\Rset^{d+1})$,
    indeed, its inverse is $\Phi_f^{-1}:(t,x)\in\Rset^{d+1}\mapsto (t,x+\mathbf{s}_0(t)-s(t)) $ and is continuously differentiable.
     Moreover, we have $\Pi_{\gamma,f}.\msg(\mathbf{s}_0)=\{(\gamma(t),s\circ \gamma(t)):\eqsp t\in\msi \}=\msg(s) $.
